First, we load the necessary libraries and data.

```{r}
data <- read.csv("a1_data.csv")
head(df, n=5)
```
Next, we need to construct a skeleton for our causal models. This is basically step 2 of the PC algorithm. In other words, pairwise independence tests are performed, and variables that are deemed statistically dependent receive a bi-directed edge.

```{r}
# Load necessary packages
BiocManager::install('linAlg',force=TRUE)
install.packages("BiocManager")
install.packages("pcalg", dependencies=TRUE)
BiocManager::install("graph")
```


```{r}
install.packages("RBGL")

```

```{r}
# Perform the PC algorithm to generate a skeleton
BiocManager::install('RBGL',force= TRUE)
library(RBGL)
```

```{r}

library(pcalg)

```


Load the necessary libraries. We will use the "glasso" package for the graph lasso algorithm and the "corpcor" package for the correlation matrix.

```{r}
BiocManager::install('glasso',force= TRUE)
library(glasso)
```
```{r}
BiocManager::install('corpcor',force= TRUE)
library(corpcor)
```
Compute the correlation matrix of the data using the "cor" function. The correlation matrix is required for the graph lasso algorithm.
```{r}
cor_mat <- cor(data)
```

Apply the graph lasso algorithm using the "glasso" function. The "glasso" function returns two objects: the inverse covariance matrix and the adjacency matrix.
```{r}
result <- glasso(cor_mat, rho=0.1)
inv_cov <- result$wi
adj_mat <- result$wi != 0
```

Visualize the skeleton graph using the "qgraph" function from the "qgraph" package. The "qgraph" function creates a plot of the graph using the adjacency matrix.
```{r}
BiocManager::install('qgraph',force= TRUE)
library(qgraph)
```

```{r}
qgraph(adj_mat, layout="spring", label.cex=0.7)
```
```{r}
BiocManager::install('bnlearn',force= TRUE)
library(bnlearn) # Load the bnlearn package for Bayesian network analysis
```
```{r}
BiocManager::install('Rgraphviz',force= TRUE)
library(Rgraphviz)
```

```{r}
BiocManager::install('grid',force= TRUE)
library(grid)
```

```{r}
# Learn the structure of the Bayesian network using the GES algorithm
bn <- gs(data)

# Print the graph structure of the Bayesian network
graphviz.plot(bn)

# Generate the Bayesian network from the learned structure
bn.fit <- bn.fit(bn, data)

# Print the conditional probability tables of the Bayesian network
print(bn.fit$cpt)
```








